Crossing Origins by Crossing Formats

### 2012-11-29 main.tex
realed work

\usepackage{listings}

@@

>>>>

% From ASIACCS'13 CFP
% Submissions must be written in English, and must be at most 10 pages
% excluding the bibliography and well-marked appendices, and at most
% 12 pages overall.

\usepackage{listings}
\usepackage{url}

@@

Backes et al.~\cite{Backes+:SP07} explore the power of the PostScript
language. PostScript allows executable content and access to sensitive
information from the environment such as the user id. This work
demonstrates how to compromise reviewer anonymity in a peer-reviewing
process by maliciously crafting a PostScript document.

Nagra~\cite{Nagra:09} demonstrates GIF/JavaScript polyglots by the
same file being interpreted as a script and as an image and
informally discuses possible security implications.

Barth et al.~\cite{Barth+:SP09}

Sundareswaran and Squicciarini~\cite{Sundareswaran:Squicciarini:CEAS10}
